Centralized Programming for Distributed Control Planes

### 2016-01-26 paper/evaluation.tex
Writeup compilation times for DC, use nodes not pods.

@@

\todo{Talk about results now}

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/compilation-times-dc.png}
\label{fig:compilation-times-dc}
\caption{Data center compilation times. \todo{change pod size to number of routers}}
\end{figure}

>>>>

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{figures/compilation-times-dc.png}
\label{fig:compilation-times-dc}
\caption{Data center compilation times.}
\end{figure}

@@

All experiments are run on an 8 core, 3.6 GHz Intel Xeon processor running Windows 7. 
%
For the data center policy, we measure the mean compilation time per-prefix since the \sysname compiler can compile for each prefix independently, and in parallel. Figure~\ref{fig:compilation-times-dc} shows the compilation times for data centers of different sizes, broken down by compilation phase. No individual compilation phase dominates the running time of the compiler, with construction and minimization of the product graph taking the most time. \sysname compiles each data center in under 15 seconds per-prefix on average. Total compilation time for the largest data center with (>1600) routers takes less than 9 minutes total.
\todo{Core compilation times here}

\ryan{Do we want to include this?}
The naive compilation algorithm from \S\ref{sec:compilation} generates extremely large ABGP policies. To offset this, the compiler performs configuration minimization both during and after configuration generation. Such minimization is useful for limiting the computational expense of matching routes on BGP routers, reducing the number of forwarding entries in routers in certain cases, and making configurations more readable for humans. Figure~\ref{fig:compilation-compress-dc} shows the effect of minimization for the data center policy. Minimization significantly reduces the size of the naive configurations.
